---
title: "botanical_garden"
author: "Shansh"
date: "Tuesday, September 29, 2015"
output: html_document
---


This is the example of webscraping data from official website of Botanical garden of Medicinal Plants - "Akademik Dr. Jovan Tucakov", Valjevo, Serbia.


```{r}
library(XML)
url <- "http://www.bastalekbiljava.rs/pages/garden-map.php"
html <- htmlTreeParse(url, useInternalNodes = T)
raw <- xpathSApply(html, "//td", xmlValue)
names <- xpathSApply(html, "//th", xmlValue)
lngt <- length(raw)
table <- data.frame(raw[seq(1, lngt, 5)], raw[seq(2, lngt, 5)], raw[seq(3, lngt, 5)], raw[seq(4, lngt, 5)], raw[seq(5, lngt, 5)])
colnames(table) <- names
write.table(table, file = "botanical_garden.txt", sep = ",", col.names = colnames(table))
```

Here are first few rows of the output.

```{r, echo=FALSE}
head(table)
```

NOTE that this database is in developnemt phase and that not all 'common names' for plant species have been entered. Furthermore, column 'Details' is sufficient in this scraping, since it contains no data (only 'more' values), but I've included anyway.
